---
title: "PLAY QA Summary"
subtitle: "Site"
date: today
format: html
params:
  vol_id: 1657
  site_id: "PENNS" 
---

## About

This report summarizes the quality assurance checks run on the PLAY data collection site.

Link to (**`r params$site_id`**) source volume: `r paste0("<https://databrary.org/volume/", params$vol_id, ">")`

## Setup

### Source functions

```{r}
#| label: source-functions
#| include: false
fl <- list.files("R", "*.R$", full.names = TRUE)
purrr::map(fl, source) |>
  purrr::quietly()
```

## Load packages

```{r}
#| label: load-packages
#| echo: false
suppressPackageStartupMessages(library(databraryr))
suppressPackageStartupMessages(library(tidyselect))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(dplyr))
```

### Log in

::: {.callout-important}
## Secure Databrary API access

This workflow requires that the user has permission to use the Databrary secure API, has created appropriate credentials on their Databrary user account, and has saved those credentials locally in `~/.Renviron`.
:::

```{r}
#| label: login-databrary
#| echo: false
login_ok <- databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

### Validate input parameters

```{r}
#| label: tbl-validate-input-parameters
vol_id_is_number <- assertthat::is.number(params$vol_id)
vol_id_gt_0 <- assertthat::assert_that(params$vol_id > 0)
site_id_is_string <- assertthat::is.string(params$site_id)
site_id_has_5_chars <- assertthat::assert_that(stringr::str_length(params$site) == 5)

input_df <- tibble::tibble(
  vol_id = as.character(params$vol_id),
  vol_id_number_ok = as.character(vol_id_is_number),
  vol_id_gt_0_ok = as.character(vol_id_gt_0),
  this_site_id = as.character(params$site_id),
  site_id_string_ok = as.character(site_id_is_string),
  site_id_5_chars_ok = as.character(site_id_has_5_chars)
)

input_df |>
  dplyr::mutate(
    vol_id = paste0(
      "<a href='https://databrary.org/volume/",
      params$vol_id,
      "'>",
      vol_id,
      "</a>"
    )
  ) |>
  tidyr::pivot_longer(cols = everything(),
                      names_to = "checks",
                      values_to = "status") |>
  dplyr::mutate(status = cell_spec(status, "html", bold = ifelse(status == "FALSE", TRUE, FALSE))) |>
  
  kableExtra::kbl(format = 'html', escape = FALSE) |>
  kableExtra::scroll_box(width = "100%", fixed_thead = TRUE) 
```

## Volume-wide checks

```{r}
#| label: get-volume-by-id
#| echo: false

if (login_ok) {
  vol_df <- databraryr::get_volume_by_id(vol_id = params$vol_id)
  vol_sessions <- databraryr::list_volume_sessions(vol_id = params$vol_id)
} else {
  warning("Databrary login failed. Skipping.")
}
```

```{r}
#| label: volume-checks
#| echo: false

if (login_ok) {
  session_releases <- xtabs( ~ session_release, vol_sessions)
  vol_checks <- tibble::tibble(
    vol_name = vol_df$title,
    name_ok = as.character(vol_name_format_ok(vol_df)),
    sharing_level = as.character(vol_df$sharing_level),
    sharing_level_ok = as.character(vol_sharing_level_ok(vol_df)),
    funding_info_ok = as.character(vol_funding_ok(vol_df)),
    has_sessions = as.character(sessions_exist(vol_sessions)),
    n_sessions = as.character(n_sessions(vol_sessions)),
    n_learning_aud = as.character(session_releases['learning_audiences']),
    n_auth_users = as.character(session_releases['authorized_users']),
    n_private = as.character(session_releases['private']),
    pct_sess_shareable = as.character(format(round(
      100 * (session_releases['learning_audiences'] + session_releases['authorized_users']) /
        n_sessions(vol_sessions),
      2
    ), nsmall = 1))
  )
  
  vol_checks |>
    tidyr::pivot_longer(cols = everything(),
                        names_to = "checks",
                        values_to = "status") |>
    dplyr::mutate(status = cell_spec(status, "html", bold = ifelse(status == "FALSE", TRUE, FALSE))) |>
    kableExtra::kbl(format = 'html', escape = FALSE) |>
    kableExtra::scroll_box(width = "100%", fixed_thead = TRUE)
} else {
  warning("Databrary login failed. Skipping.")
}
```

## Session checks

```{r}
#| label: session-checks
#| echo: false

if (login_ok) {
  session_folder_prefix <- make_session_folder_prefix(params$vol_id)
  session_name_checks <- tibble::tibble(
    session_name_prefix = session_folder_prefix,
    name_prefix_ok = as.character(
      session_prefix_names_ok(vol_sessions, prefix = session_folder_prefix)
    ),
    name_suffix_ok = as.character(
      session_suffix_names_ok(vol_sessions, prefix = session_folder_prefix)
    )
  )
  
  session_name_checks |>
    tidyr::pivot_longer(everything(), names_to = "checks", values_to = "status") |>
    dplyr::mutate(status = cell_spec(status, "html", bold = ifelse(status == "FALSE", TRUE, FALSE))) |>
    kableExtra::kbl(format = 'html', escape = FALSE) |>
    kableExtra::scroll_box(width = "100%", fixed_thead = TRUE)
  
} else {
  warning("Databrary login failed. Skipping.")
}
```

### Session file checks

```{r}
#| label: session-file-checks
#| echo: false

if (login_ok) {
  session_checks_df <- purrr::map2(
    vol_sessions$session_id,
    vol_sessions$session_name,
    check_session_files,
    vol_id = params$vol_id
  ) |>
    purrr::list_rbind() |>
    dplyr::arrange(session_name)
} else {
  warning("Databrary login failed. Skipping.")
}
```

```{r}
#| label: tbl-session-file-checks
#| echo: false

session_file_check <- function(status) {
  not_na <- !is.na(status)
  gt0 <- status > 0
  not_na & gt0
}

if (login_ok) {
session_checks_df |>
  dplyr::mutate(
    session_id = paste0(
      "<a href='https://databrary.org/volume/",
      params$vol_id,
      "/session/",
      session_id,
      "'>",
      session_id,
      "</a>"
    )
  ) |>
  dplyr::mutate(natural_play = cell_spec(natural_play, "html", 
                                         bold = ifelse(session_file_check(natural_play), 
                                                       FALSE, TRUE))) |>
  dplyr::mutate(house_walkthru = cell_spec(house_walkthrough, "html", 
                                          bold = ifelse(session_file_check(house_walkthrough), 
                                                            FALSE, TRUE))) |>
    dplyr::mutate(struct_play = cell_spec(structured_play, "html",
                                              bold = ifelse(session_file_check(structured_play), 
                                                            FALSE, TRUE))) |>
  dplyr::mutate(questionnaires = cell_spec(questionnaires, "html", 
                                           bold = ifelse(session_file_check(questionnaires),
                                                         FALSE, TRUE))) |>
  dplyr::mutate(decibel = cell_spec(decibel, "html", 
                                    bold = ifelse(session_file_check(decibel), FALSE, TRUE))) |>
  dplyr::mutate(release_levels = cell_spec(release_levels, "html",
                                          bold = ifelse(session_file_check(release_levels), 
                                                        FALSE, TRUE))) |>
  kableExtra::kbl(format = 'html', escape = FALSE) |>
  kableExtra::scroll_box(width = "100%", fixed_thead = TRUE)  
} else {
  warning("Databrary login failed. Skipping.")
}

```

## Folder checks

```{r}
#| label: folder-checks
#| echo: false

if (login_ok) {
  vol_folders <- databraryr::list_volume_folders(vol_id = params$vol_id)
  
  vol_folder_checks <- tibble::tibble(
    vol_has_folders = as.character(folders_exist(vol_folders)),
    vol_n_folders = as.character(n_folders(vol_folders)),
    vol_name_ok = as.character(folder_name_ok(vol_folders)),
    vol_release_ok = as.character(folder_release_level_ok(vol_folders)),
    vol_folder_contains_demog = as.character(
      folder_contains_demog_file(vol_folders, params$vol_id, session_folder_prefix)
    ),
    vol_demog_file_release_ok = as.character(demog_file_release_ok(vol_folders, 
                                                                   params$vol_id))
  )
  
  vol_folder_checks |>
    tidyr::pivot_longer(cols = starts_with("vol"), 
                        names_to= "checks", values_to = "status") |>
    kableExtra::kbl(format = 'html', escape = FALSE) |>
    kableExtra::scroll_box(width = "100%", fixed_thead = TRUE)
} else {
  warning("Databrary login failed. Skipping.")
}
vol_folders <- databraryr::list_volume_folders(vol_id = params$vol_id
)
```

## Log out

```{r}
databraryr::logout_db()
```
