---
title: "PLAY QA Summary"
format: html
params:
  vol_id: 1657
  site_id: "PENNS"
---

## About

This report summarizes the quality assurance checks run on the PLAY data collection site.

Collection site: **`r params$site_id`**

Link to source volume: `r paste0("<https://databrary.org/volume/", params$vol_id, ">")`

## Setup

### Source functions

```{r}
#| label: source-functions
#| echo: false
fl <- list.files("R", "*.R$", full.names = TRUE)
purrr::map(fl, source) |>
  purrr::quietly()
```

## Load packages

```{r}
#| label: load-packages
#| echo: false
suppressPackageStartupMessages(library(databraryr))
```

### Log in

::: {.callout-important}
## Secure Databrary API access

This workflow requires that the user has permission to use the Databrary secure API, has created appropriate credentials on their Databrary user account, and has saved those credentials locally in `~/.Renviron`.
:::

```{r}
#| label: login-databrary
#| echo: false
databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Volume-wide checks

```{r}
#| label: get-volume-by-id
#| echo: false
vol_df <- databraryr::get_volume_by_id(vol_id = params$vol_id)
vol_sessions <- databraryr::list_volume_sessions(vol_id = params$vol_id)
```

```{r}
#| label: volume-checks
#| echo: false
message("Volume name OK: ", vol_name_format_ok(vol_df))
message("Volume sharing level OK: ", vol_sharing_level_ok(vol_df))
message("Volume sharing level: ", vol_df$sharing_level)
message("Volume funding info OK: ", vol_funding_ok(vol_df))
message("--------------")
message("Sessions exist? ", sessions_exist(vol_sessions))
message("Volume has n= ", n_sessions(vol_sessions), " sessions")
session_releases <- xtabs(~ session_release, vol_sessions)
message("\tLearning audiences: n= ", session_releases['learning_audiences'], " sessions")
message("\tAuthorized users: n= ", session_releases['authorized_users'], " sessions")
message("\tPrivate: n= ", session_releases['private'], " sessions")
message("Percent sharable: ", format(100*(session_releases['learning_audiences'] + session_releases['authorized_users'])/n_sessions(vol_sessions), 1))
```

## Session checks

```{r}
#| label: session-checks
#| echo: false

session_folder_prefix <- make_session_folder_prefix(params$vol_id)
message("Target session name prefix: '", session_folder_prefix, "'")
message(
  "Session name prefixes OK: ",
  session_prefix_names_ok(vol_sessions, prefix = session_folder_prefix)
)
message(
  "Session name suffixes OK: ",
  session_suffix_names_ok(vol_sessions, prefix = session_folder_prefix)
)
```

### Session file checks

```{r}
#| label: session-file-checks
#| echo: false
session_checks_df <- purrr::map2(
  vol_sessions$session_id,
  vol_sessions$session_name,
  check_session_files,
  vol_id = params$vol_id) |>
  purrr::list_rbind()
```

```{r}
#| label: tbl-session-file-checks
#| echo: false
session_checks_df |>
  dplyr::mutate(
    session_id = paste0(
      "<a href='https://databrary.org/volume/",
      params$vol_id,
      "/session/",
      session_id,
      "'>",
      session_id,
      "</a>"
    )
  ) |>
  kableExtra::kbl(format = 'html', escape = FALSE) |>
  kableExtra::scroll_box(width = "100%", height = "500px", fixed_thead = TRUE)
```

## Folder checks

```{r}
#| label: folder-checks
#| echo: false
vol_folders <- databraryr::list_volume_folders(vol_id = params$vol_id)

message("Folder(s) exist? ", folders_exist(vol_folders))
message("N= ", n_folders(vol_folders), " folders")
message("Folder name OK: ", folder_name_ok(vol_folders))
message("Folder release level OK: ",
        folder_release_level_ok(vol_folders))
message(
  "Folder contains demographic file: ",
  folder_contains_demog_file(vol_folders, params$vol_id, session_folder_prefix)
)
message(
  "Demographic file has correct release level: ",
  demog_file_release_ok(vol_folders, params$vol_id)
)
```

## Log out

```{r}
databraryr::logout_db()
```
