---
title: "Site Volume QA"
format: html
---

## About

This page documents Rick Gilmore's work to develop a PLAY site-specific volume
quality assurance (QA) workflow.

## Setup

::: {.callout-important}
## Secure Databrary API access

This workflow requires that the user has permission to use the Databrary secure API, has created appropriate credentials on their Databrary user account, and has saved those credentials locally in `~/.Renviron`.
:::

### Log in

```{r}
databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Target Penn State volume

Most of the functions we need require that we specify the target volume ID (`vol_id`).

```{r}
VOLUME_ID <- 1657
```

### Volume checks

```{r}
vol_df <- databraryr::get_volume_by_id(vol_id = VOLUME_ID)
```

Does the volume title follow the project convention?

::: {.callout-note}
The name 'prefix' contains "PLAYProject_" and the 'postfix' is a 5-chararacter string with all capital letters or a number.
:::

```{r}
vol_name_ok <- function(vol_df) {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "title")
  prefix <- "PLAYProject_"
  prefix_ok <- stringr::str_detect(vol_df$title, paste0("^", prefix))
  postfix_ok <- stringr::str_detect(vol_df$title, "[A-Z1-2]{5}$")
  prefix_ok & postfix_ok
}

vol_name_ok(vol_df)
```

Is the volume sharing level ok?

```{r}
vol_sharing_level_ok <- function(vol_df, sharing_level = "public_overview_only") {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "sharing_level")
  assertthat::is.string(sharing_level)
  assertthat::assert_that(sharing_level %in% c("public", "public_overview_only"))
  vol_df$sharing_level == sharing_level
}

vol_sharing_level_ok(vol_df)
```

Is funder information correct?

::: {.callout-important}
The funder should be consistent across the site specific volumes.

**TODO**: Determine what that funder information should be.
:::

```{r}
vol_funding_ok <- function(vol_df) {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "fundings")
  funding_not_empty <- (length(vol_df$fundings[[1]]) > 0)
  funding_not_empty
}

vol_funding_ok(vol_df)
```

## Session checks

```{r}
make_session_folder_prefix <- function(vol_id) {
  assertthat::is.number(vol_id)
  assertthat::assert_that(vol_id > 0)
  
  vol_df <- databraryr::get_volume_by_id(vol_id = vol_id)
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "title")
  
  paste0("PLAY_", stringr::str_extract(vol_df$title, "[A-Z1-2]{5}$"), "_")
}

make_session_folder_prefix(VOLUME_ID)
```

Are there sessions?

```{r}
vol_sessions <- databraryr::list_volume_sessions(vol_id = VOLUME_ID)

sessions_exist <- function(vol_sessions) {
  assertthat::assert_that(!is.null(vol_sessions))
  dim(vol_sessions)[1] > 0
}

n_sessions <- function(vol_sessions) {
  assertthat::assert_that(!is.null(vol_sessions))
  dim(vol_sessions)[1]
}

sessions_exist <- function(vol_sessions) {
  n_sessions(vol_sessions) > 0
}

sessions_exist(vol_sessions)
n_sessions(vol_sessions)
```

### Session release levels

```{r}
xtabs(~ session_release, vol_sessions)
```

### Session names

Session name(s) follow standard.

```{r}
folder_name_ok <- function(vol_folders, prefix = "PLAY_PENNS_") {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::has_name(vol_folders, "folder_name")
  assertthat::is.string(prefix)
  
  names <- vol_folders$folder_name
  stringr::str_detect(names, "demographics")
  
  prefix_ok <- stringr::str_detect(names, paste0("^", prefix))
  postfix_ok <- stringr::str_detect(names, "demographics$")
  prefix_ok & postfix_ok
}

session_name_suffix_ok <- function(name) {
  assertthat::is.string(name)
  
  suffix <- stringr::str_extract(name, "[0-9]{3}$")
  as.numeric(suffix) > 0
}

session_name_prefix_ok <- function(name, prefix) {
  assertthat::is.string(name)
  assertthat::is.string(prefix)
  session_prefix <- stringr::str_extract(name, paste0("PLAY_[A-Z0-9]{5}_"))
  prefix == session_prefix
}

session_name_prefix_ok(vol_sessions$session_name[1], 
                       prefix = make_session_folder_prefix(VOLUME_ID))

session_name_suffix_ok(vol_sessions$session_name[1])
```

Check all sessions.

```{r}
session_folder_prefix <- make_session_folder_prefix(VOLUME_ID)
# purrr::map(vol_sessions$session_name, session_name_prefix_ok, prefix = session_folder_prefix) |> purrr::list_c()

session_prefix_names_ok <- function(vol_sessions, prefix) {
  prefixes_ok <- purrr::map(vol_sessions$session_name, session_name_prefix_ok, prefix = prefix) |> 
    purrr::list_c()
  sum(prefixes_ok) == length(prefixes_ok)
}

session_prefix_names_ok(vol_sessions, prefix = session_folder_prefix)
```

```{r}
session_suffix_names_ok <- function(vol_sessions, prefix) {
  suffixes_ok <- purrr::map(vol_sessions$session_name, session_name_suffix_ok) |> 
    purrr::list_c()
  sum(suffixes_ok) == length(suffixes_ok)
}

session_suffix_names_ok(vol_sessions, prefix = session_folder_prefix)
```

### Session contents

::: {.callout-important}
## Criteria

1. Each session should contain one or more video files (.mp4) with the following name format: "PLAY_<SITE_ID>_NaturalPlay.mp4".
2. Each session should contain a video file (.mp4) with the following name format: "PLAY_<SITE_ID>_HouseWalkThrough.mp4".
3. Each session should contain a video file (.mp4) with the following name format: "PLAY_<SITE_ID>_StructuredPlay.mp4".
4. Each session should (optionally) contain a video file (.mp4) with the following name format: "PLAY_<SITE_ID>_Questionnaires.mp4"
5. Each session should contain a CSV file with the following name format: "PLAY_<SITE_ID>_Decibel.csv"
6. Each file in each session should have the same release level as the parent session.
:::

```{r}
a_session <- vol_sessions[2,]
session_assets <- databraryr::list_session_assets(a_session$session_id, vol_id = VOLUME_ID)
file_prefix <- paste0(a_session$session_name, "_")
```

```{r}
video_exists <- function(session_assets, prefix = NULL, suffix = NULL) {
  assertthat::assert_that(!is.null(session_assets))
  assertthat::has_name(session_assets, "asset_name")
  assertthat::is.string(prefix)
  assertthat::is.string(suffix)
  
  asset_names <- session_assets$asset_name
  target_fn <- paste0(prefix, suffix)
  if (!(target_fn %in% asset_names)) {
    0
  } else {
  sum(target_fn %in% asset_names)
  }
}

naturalPlay_video_exists <- function(session_assets, prefix, suffix = "NaturalPlay") {
  video_exists(session_assets = session_assets, prefix = prefix, suffix = suffix)
}

naturalPlay_video_exists(session_assets, prefix = file_prefix)
```

```{r}
houseWalkthrough_video_exists <- function(session_assets, prefix, suffix = "HouseWalkthrough") {
  video_exists(session_assets = session_assets, prefix = prefix, suffix = suffix)
}
houseWalkthrough_video_exists(session_assets, prefix = file_prefix)
```

```{r}
structuredPlay_video_exists <- function(session_assets, prefix, suffix = "StructuredPlay") {
  video_exists(session_assets = session_assets, prefix = prefix, suffix = suffix)
}
structuredPlay_video_exists(session_assets, prefix = file_prefix)
```

```{r}
questionnaires_video_exists <- function(session_assets, prefix, suffix = "Questionnaires") {
  video_exists(session_assets = session_assets, prefix = prefix, suffix = suffix)
}
questionnaires_video_exists(session_assets, prefix = file_prefix)
```

```{r}
decibel_exists <- function(session_assets, prefix, suffix = "Decibel") {
  video_exists(session_assets = session_assets, prefix = prefix, suffix = suffix)
}
```

```{r}
file_release_matches_session <- function(session_assets = NULL, session_release = NULL) {
  assertthat::assert_that(!is.null(session_assets))
  assertthat::has_name(session_assets, "asset_permission")
  assertthat::is.string(session_release)

  releases_match <- (session_release %in% session_assets$asset_permission)
  length(releases_match) == sum(releases_match)
}

file_release_matches_session(session_assets, a_session$session_release)
```

```{r}
get_session_release <- function(this_session_id, vol_id) {
  assertthat::is.number(this_session_id)
  assertthat::assert_that(this_session_id > 0)
  assertthat::is.number(vol_id)
  assertthat::assert_that(vol_id > 0) 
  
  this_session <- databraryr::list_volume_sessions(vol_id = vol_id) |>
    dplyr::filter(session_id == this_session_id)
  
  assertthat::assert_that(!is.null(this_session))
  assertthat::has_name(this_session, "session_release")
  assertthat::is.string(this_session$session_release)
  this_session$session_release
}

get_session_release(a_session$session_id, VOLUME_ID)
```


Chunk through all sessions.

```{r}
check_session_files <- function(session_id = NULL, session_name = NULL, 
                                vol_id = NULL) {
  assertthat::is.number(session_id)
  assertthat::assert_that(session_id > 0)
  assertthat::is.number(vol_id)
  assertthat::assert_that(vol_id > 0)

  file_prefix <- paste0(session_name, "_")
  assertthat::is.string(file_prefix)
  
  natural_play <- NA
  house_walkthrough <- NA
  structured_play <- NA
  questionnaires <- NA
  decibel <- NA
  release_levels <- NA
  
  session_release <- get_session_release(session_id, VOLUME_ID)
  assertthat::is.string(session_release)
  
  session_assets <- databraryr::list_session_assets(session_id, vol_id = vol_id)

  if (!is.null(session_assets)) {
    natural_play <- naturalPlay_video_exists(session_assets, prefix = file_prefix)
    house_walkthrough <- houseWalkthrough_video_exists(session_assets, prefix = file_prefix)
    structured_play <- structuredPlay_video_exists(session_assets, prefix = file_prefix)
    questionnaires <- questionnaires_video_exists(session_assets, prefix = file_prefix)
    decibel <- decibel_exists(session_assets, prefix = file_prefix)
    release_levels <- file_release_matches_session(session_assets, session_release)
  }
  
  tibble::tibble(
    session_id = session_id,
    session_name = session_name,
    natural_play = natural_play,
    house_walkthrough = house_walkthrough,
    structured_play = structured_play,
    questionnaires = questionnaires,
    decibel = decibel,
    release_levels = release_levels
  )
}

check_session_files(a_session$session_id, a_session$session_name, vol_id = VOLUME_ID)
```

```{r}
purrr::map2(vol_sessions$session_id,
            vol_sessions$session_name,
            check_session_files,
            vol_id = VOLUME_ID,
            .progress = paste0("N=", dim(vol_sessions)[1], " sessions...")) |>
  purrr::list_rbind()
```

### Session metadata

::: {.callout-warning}
## Under construction

This section is under construction.
:::

## Folder checks

```{r}
folders <- databraryr::list_volume_folders(vol_id = VOLUME_ID)
```

Are there folders?

```{r}
vol_folders <- databraryr::list_volume_folders(vol_id = VOLUME_ID)

folders_exist <- function(vol_folders) {
  assertthat::assert_that(!is.null(vol_folders))
  dim(vol_folders)[1] > 0
}

folders_exist(vol_folders)
```

Is there only one folder?

```{r}
only_one_folder <- function(vol_folders) {
  assertthat::assert_that(!is.null(vol_folders))
  dim(vol_folders)[1] == 1
}

only_one_folder(vol_folders)
```

### Names

Folder name follows standard.

```{r}
folder_name_contains_demographics <- function(vol_folders) {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::has_name(vol_folders, "folder_name")
  names <- vol_folders$folder_name
  sum(stringr::str_detect(names, "demographics")) == length(names)
}

folder_name_contains_demographics(vol_folders)
```

```{r}
folder_name_ok <- function(vol_folders, prefix = "PLAY_PENNS_") {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::has_name(vol_folders, "folder_name")
  assertthat::is.string(prefix)
  
  names <- vol_folders$folder_name
  stringr::str_detect(names, "demographics")
  
  prefix_ok <- stringr::str_detect(names, paste0("^", prefix))
  postfix_ok <- stringr::str_detect(names, "demographics$")
  prefix_ok & postfix_ok
}

folder_name_ok(vol_folders)
```

### Release level

Does the folder have a release level set to "authorized_users"

```{r}
folder_release_level_ok <- function(vol_folders) {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::has_name(vol_folders, "folder_release")
  vol_folders$folder_release == "authorized_users"
}

folder_release_level_ok(vol_folders)
```

### Files

Does the folder contain a demographics file?

```{r}

folder_contains_demog_file <- function(vol_folders, vol_id, file_prefix) {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::is.number(vol_id)
  assertthat::assert_that(vol_id > 0)
  
  folder_assets <- databraryr::list_folder_assets(folder_id = vol_folders$folder_id, 
                                      vol_id = vol_id)
  assertthat::assert_that(!is.null(folder_assets))
  
  paste0(session_folder_prefix, "demographics") %in% folder_assets$asset_name
}

folder_contains_demog_file(vol_folders, VOLUME_ID, session_folder_prefix)
```

Does the file have the proper release level?

```{r}
demog_file_release_ok <- function(vol_folders, vol_id) {
  assertthat::assert_that(!is.null(vol_folders))
  assertthat::is.number(vol_id)
  assertthat::assert_that(vol_id > 0)
  
  folder_assets <- databraryr::list_folder_assets(folder_id = vol_folders$folder_id, 
                                      vol_id = vol_id)
  assertthat::assert_that(!is.null(folder_assets))
  
  demog_file <- folder_assets |>
    dplyr::filter(stringr::str_detect(asset_name, "demographics"))
  
  demog_file$asset_permission == "authorized_users"
}

demog_file_release_ok(vol_folders, VOLUME_ID)
```

## Interim summary report

```{r}
message("Volume name OK: ", vol_name_ok(vol_df))
message("Volume sharing level OK: ", vol_sharing_level_ok(vol_df))
message("Volume funding info OK: ", vol_funding_ok(vol_df))
message("Sessions exist? ", sessions_exist(vol_sessions))
message("Session name prefixes OK: ", session_prefix_names_ok(vol_sessions, prefix = session_folder_prefix))
message("Session name suffixes OK: ", session_suffix_names_ok(vol_sessions, prefix = session_folder_prefix))
message("Folder(s) exist? ", folders_exist(vol_folders))
message("Folder name OK: ", folder_name_ok(vol_folders))
message("Folder release level OK: ", folder_release_level_ok(vol_folders))
message("Folder contains demographic file: ", folder_contains_demog_file(vol_folders, VOLUME_ID, session_folder_prefix))
message("Demographic file has correct release level: ", demog_file_release_ok(vol_folders, VOLUME_ID))
```

## Clean up

### Log out

```{r}
databraryr::logout_db()
```
