---
title: "Site Volume QA"
format: html
---

## About

This page documents Rick Gilmore's work to develop a PLAY site-specific volume
quality assurance (QA) workflow.

## Setup

::: {.callout-important}
## Secure Databrary API access

This workflow requires that the user has permission to use the Databrary secure API, has created appropriate credentials on their Databrary user account, and has saved those credentials locally in `~/.Renviron`.
:::

### Log in

```{r}
databraryr::login_db(email = Sys.getenv("DATABRARY_LOGIN"),
         password = Sys.getenv("DATABRARY_PASSWORD"),
         client_id = Sys.getenv("DATABRARY_CLIENT_ID"),
         client_secret = Sys.getenv("DATABRARY_CLIENT_SECRET"),
         store = FALSE,
         overwrite = FALSE)
```

## Target Penn State volume

Most of the functions we need require that we specify the target volume ID (`vol_id`).

```{r}
VOLUME_ID <- 1657
```

### Volume summary

```{r}
vol_df <- databraryr::get_volume_by_id(vol_id = VOLUME_ID)
```

Does the volume title follow the project convention?

::: {.callout-note}
The name 'prefix' contains "PLAYProject_" and the 'postfix' is a 5-chararacter string with all capital letters or a number.

```{r}
vol_name_ok <- function(vol_df) {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "title")
  prefix <- "PLAYProject_"
  prefix_ok <- stringr::str_detect(vol_df$title, paste0("^", prefix))
  postfix_ok <- stringr::str_detect(vol_df$title, "[A-Z1-2]{5}$")
  prefix_ok & postfix_ok
}
```

Is the volume sharing level ok?

```{r}
vol_sharing_level_ok <- function(vol_df, sharing_level = "public_overview_only") {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "sharing_level")
  assertthat::is.string(sharing_level)
  assertthat::assert_that(sharing_level %in% c("public", "public_overview_only"))
  vol_df$sharing_level == sharing_level
}
```

Is funder information correct?

::: {.callout-important}
The funder should be consistent across the site specific volumes.

**TODO**: Determine what that funder information should be.
:::

```{r}
vol_funding_ok <- function(vol_df) {
  assertthat::assert_that(!is.null(vol_df))
  assertthat::has_name(vol_df, "fundings")
  
  
}
```


## Clean up

### Log out

```{r}
databraryr::logout_db()
```
